\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
explain why we don't DCE

\section{Surprises and Lessons Learned}
%% XXX: TODO
%% Were any of your results surprising our counter-intuitive? If so, what did you learn from those surprises? What did you learn from this experience in general?
Boy, JS is a pain in the ass.
This is a lesson learned, not a surprise.

@@

A number of further optimizations are possible using our range
analysis framework. If the range associated with an instruction
becomes empty, then the block has been proven dead and can be
eliminated. Control flow operations can be proven redundant as well,
further eliminating computation and dead basic blocks. These graph
manipulations are currently not available in the IonMonkey compiler,
which is in active development but not yet complete.

>>>>

@@

A number of Further optimizations are possible using our range analysis
framework. If the range associated with an instruction becomes empty, then the
block has been proven dead and can be eliminated. Control flow operations can
be proven redundant as well, further eliminating computation and dead basic
blocks. These graph manipulations are currently not available in the IonMonkey
compiler, which is in active development but not yet complete. There are a
variety of reasons for this current design restriction. IonMonkey must
integrate very closely with the interpreter and the JS runtime, and so
generated code must maintain a careful correspondence with the interpreter.
This means that eliminating control flow is a non-trivial
operation\cite{dvander}.
